---
title: "Data Overview"
author: "Kirsten Scherer Auberson"
date: "3/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setwd("/Volumes/documents/MasterThesis/reports")
#install.packages("knitr")
library("knitr")
#In a terminal: ruby -e "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/master/install)" < /dev/null 2> /dev/null
#then:
#devtools::install_github("jimhester/archive")
library(archive)
library(XML)
```

## Archive structure

The dataset consists of a small number of regular files:
```{r nonarchives, echo=TRUE}
setwd("../data/raw/stackexchange")
regularfiles <- grep(list.files(include.dirs=F), pattern="7z$", inv=T, value=T)
regularfilesSize <- round(file.size(regularfiles)/1024, digits=0)

dataframe <- data.frame(name=regularfiles, size=regularfilesSize)
kable(dataframe[order(dataframe$size, decreasing = T),], row.names = F)
```

(All sizes in KB)

And a large number of 7-zip archives:
```{r archives, echo=TRUE}
setwd("../data/raw/stackexchange")
archives <- grep(list.files(include.dirs=F), pattern="7z$", inv=F, value=T)
archivesFilecount <- unlist(lapply(archives, function(s) length(archive::archive(s)$path)))
archivesSize <- round(file.size(archives)/1024, digits=0)

dataframe <- data.frame(name=archives, files=archivesFilecount, size=archivesSize)
kable(dataframe[order(dataframe$size, decreasing = T),], row.names = F)
```

(All sizes in KB)

## Contents of the archives:

A typical archive contains 8 XML files:
```{r archiveContent, echo=TRUE}
kable(archive::archive("../data/raw/stackexchange/math.stackexchange.com.7z"))
```

Many archives are accompanied by a 'meta' archive, containing the same files. These are sites that serve questions about a particular sites, e.g. the math meta site would answer questions about the math site, not about mathematics:
```{r metaArchiveContent, echo=TRUE}
kable(archive::archive("../data/raw/stackexchange/math.meta.stackexchange.com.7z"))
```

The archives starting in "stackoverflow.com-" are special archives that contain a single XML file with data that is either aggregated, or common to the entire site, such as the user names: 
```{r singleArchiveContent, echo=TRUE}
kable(archive::archive("../data/raw/stackexchange/stackoverflow.com-Users.7z"))
```

## Structure of the XML files:

```{r posts, echo=TRUE}
cooking <- archive::archive_read("../data/raw/stackexchange/cooking.stackexchange.com.7z")
file <- xmlParse(readLines(archive::archive_read(cooking, "Posts.xml")), options = HUGE)
dataframe <- xmlToDataFrame(readLines(archive::archive_read(cooking, "Posts.xml")))

```